A New Metric for the Analysis of Swarms

### 2018-06-13 paper.tex

\begin{abstract}
  % An important criterion in the assessment of swarm coordination algorithms is
  % the extent to which they cause unnecessary movement, i.e. movement which
  % occurs as a side effect of the algorithm rather than from the fulfilment of
  % the intended function of the swarm. 
  A widely used metric for the assesment of swarm coordination algortithms is a metric based upon the distance between agents.
  This paper examines this metric and introduces an entirely new metric based upon the magnitude of cohesion and repulsion between agents, comparing and
  contrasting the two.  
  The \emph{cohesion/repulsion} metric offers a
  number of advantages over the distance metric. The
  \emph{cohesion/repulsion} metric allows the identification of the
  essential characteristic of a swarm as `expanding', `stable', or
  `contracting'. This is not possible with the distance metric. Practical
  swarming applications where this might apply include area filling and reconnaissance.
\end{abstract}

@@

\section{Future work\label{metric:Future}}
The metric can be applied to the analysis of the effects of coordination algorithms upon a swarm's structure. An application to floodfilling has just been discussed. The metric can also be applied to identifying the effects a `healing' algorithm may have upon a swarm's structure. By this we mean an algorithm which removes `voids' in a swarm.

The detection of a swarm's perimeter \cite{MD:09, MJ:08, ZAPS:07, JG:13} identifies a subset of a swarm which can be used for coordination. The use of the perimeter detection allows a swarm to be used in many different ways~\cite{ZFG:13, AKK:08, APZDAMC:09, AZDPS:11}.

A possible adaptation to this area of research is to use the swarm perimeter detection to identify a subset of agents then reduce the field effects (repulsion and cohesion) of those agents to increase the agent density at the perimeter, this is similar to having heterogeneous swarm structures as shown in Fig.~\ref{additional:fieldsWork}. Increasing the density would allow increased coverage of any sensor arrays that the swarm was using at the swarm edge.

The issue with introducing heterogeneous field effects is that the existing distance-based metric would not allow the swarm's structure to be analysed correctly. We believe that cohesion/repulsion metric discussed in this paper will still identify the swarm's structure when the swarm is hetrogenious. This is due to the metric being based upon inter-agent effects rather than physical distribution.

>>>>

\begin{abstract}
  % An important criterion in the assessment of swarm coordination algorithms is
  % the extent to which they cause unnecessary movement, i.e. movement which
  % occurs as a side effect of the algorithm rather than from the fulfilment of
  % the intended function of the swarm. 
  A widely used metric for the analysis of swarm coordination algorithms is
  based upon the distance between agents. This paper examines this metric and
  introduces an entirely new metric based upon the magnitude of the cohesion
  and repulsion vectors between agents. In comparing and contrasting the two
  metrics, we find that the \emph{cohesion/repulsion} metric offers a number of
  advantages over the distance metric. In particular, the
  \emph{cohesion/repulsion} metric allows the identification of the essential
  characteristic of a swarm as `expanding', `stable', or `contracting'. This is
  not possible with the distance metric.  Practical swarming applications where
  the new metric is useful include area filling and reconnaissance.
\end{abstract}

@@

\section{Future work\label{metric:Future}}

The new metric can be applied to the analysis of the effects of coordination
algorithms upon a swarm's structure. An application to flood filling has just
been discussed. The metric can also be applied to identifying the effects of 
`healing' algorithms, e.g. to remove `voids' from a swarm. We plan
to investigate this, and other, practical applications of the metric.

The detection of a swarm's perimeter~\cite{MD:09, MJ:08, ZAPS:07, JG:13}
identifies a subset of a swarm which can be used for coordination. 
Perimeter detection is widely used in swarm coordination~\cite{ZFG:13, AKK:08,
APZDAMC:09, AZDPS:11}. A possible adaptation of this area of research is to
investigate the reduction of the field effects (cohesion and repulsion) of
agents at the perimeter, so increasing agent density in this region. Increasing
the density would allow increased coverage by the swarm at its perimeter. This
could improve the granularity of analysis, e.g. when using sensor arrays at
thr frontier of the swarm.
However, this approach leads to swarms of agents having heterogeneous field
effects, as shown in Fig.~\ref{additional:fieldsWork}. Clearly, the
distance-based metric is not useful in the analysis of such swarms. We believe
that the cohesion/repulsion metric introduced in this paper can identify a
swarm's structure even when the swarm is heterogeneous, since the metric is
based directly upon inter-agent field effects rather than the physical
distribution of agents. This will also be the subject of forthcoming work.
